A Deeper Look into Bug Fixes: Patterns, Replacements, Deletions, and Additions

### 2016-03-10 MSRChallenge2016.tex
Slightly revised Discussion
Emphasize that direct translation from C to Java may not work

Table~\ref{tab:freqpattern} estimates the prevelance of PAR templates in the
Java dataset. The most common pattern we observed is ABC (add or remove a branch condition); and the least common
pattern is AOB (adding an array out of bound checker). If we conservatively assume that these patterns never appear together, they
cover 14.78\% of buggy files. In the dataset studied by Kim et al., the overall
10 patterns cover almost 30\% of real patches~\cite{kim2013}. Although we only analyze 8
out of 10 bug fixing patterns, it is unlikely the final two will cover the
difference. Moreover, our detection is imprecise, and might represent an upper
bound.  This suggests that these fixing patterns might not generalize
beyond an initial dataset, and that more work remains to expressively characterize human bug-fixing behavior.

@@

The findings of our study provide useful insights for automatic program repair
tools in Java. It suggests that patterns proposed by the state-of-the-art in
generate and validate bug report for Java are insufficient cover the extent of
bug fixes in our dataset.  Adding more patterns is one solution, but may not be
a general one.  Our findings further suggest that
mutation based program repair may need to consider field or method insertion to
achieve human-comparability in patches.  A deeper look suggests that such
techniques may benefit from leveraging probabilistic knowledge of what types of
statements are commonly inserted, deleted, or replaced in Java bug-fixing commits.
Overall, our findings motivate additional study of 
repair in Java, as assumptions that underlie approaches that target C seem
unlikely to translate directly.

>>>>

Table~\ref{tab:freqpattern} estimates the prevelance of PAR templates in the
Java dataset. The most common pattern we observed is ABC (add or remove a branch condition); and the least common
pattern is AOB (adding an array out of bound checker). If we conservatively assume that these patterns never appear together, they
cover 14.78\% of buggy files. In the dataset studied by Kim et al., the overall
10 patterns cover almost 30\% of real patches~\cite{kim2013}. Although we only analyze 8
out of 10 bug fixing patterns, it is unlikely the final two will cover the
difference. To even get close to 30\%, each of the patterns need to cover around 7\% of buggy files and we are still assuming that the patterns never appear together. 
%Moreover, our detection is imprecise, and might represent an upper bound. 
This suggests that these fixing patterns might not generalize
beyond an initial dataset, and that more work remains to expressively characterize human bug-fixing behavior.

@@

\noindent\textbf{Lessons learned.} The findings of our study provide useful
insights for automatic program repair tools in Java. It suggests that patterns
proposed by the state-of-the-art approaches for Java are insufficient to cover
the extent of bug fixes in our dataset.  Adding more patterns is one solution,
but may not be a general one.  Our findings further suggest that mutation based
program repair may need to consider field or method insertion to achieve
human-comparability in patches. This finding indicates that direct translation
of mutation based approaches from C to Java is not likely to succeed due to the
different language constructs.  A deeper look suggests that such techniques may
benefit from leveraging probabilistic knowledge of what types of statements are
commonly inserted, deleted, or replaced in Java bug-fixing commits. Again, the
probabilistic knowledge for C is not likely to work for Java program if
different coding conventions are considered.  Overall, our findings motivate
additional study of repair in Java, as assumptions that underlie approaches that
target C seem unlikely to translate directly.
